Score-based tests of measurement invariance: Use in practice

### 2014-07-02 frontiers/IMPSpres-knitr.Rnw
update IMPSpres-knitr.Rnw and lines according to Ed's comment.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@348 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\renewcommand\bibliographytypesize{\tiny}

@@

  \begin{eqnarray}
   s(\hat{{\bm \theta}}; \bm{x}_i) = \frac{\partial}{\partial \bm{\theta}} 
  \log
\text{L}({\bm{x}}_i, {\bm{\theta}}) \big |_{\bm{\theta} = \widehat{\bm{\theta}}}\\
  \displaystyle\sum_{i=1}^{n} s(\hat{\bm{\theta}} ; \bm{x}_i) =
  {\bm 0} 
  \end{eqnarray}

@@

\end{frame}
%--------------------------------------------------------------------------
\begin{frame}[fragile]
\frametitle{Procedures of Application}
\begin{enumerate}[3.]
  \suite
  \item Test of measurement invariance
\end{enumerate}
<<sctest-ord2, eval=TRUE>>=
 library(strucchange)
wdmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4, 
               vcov = "info", functional = "WDMo", 
               plot = FALSE)
wdmo
@ 
\end{frame}
%--------------------------------------------------------------------------

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics, fig.height=3.3, fig.width=5, echo=FALSE, results='hide'>>=
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = "WDMo", plot = TRUE, 
               ylim = c(0, 3.2), xlab = "Age group", 
               ylab = "Weighted test statistics")
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
 \begin{itemize}
 \item Thanks! 
 \item Questions?
 \end{itemize}
\end{frame}
%--------------------------------------------------------------------------
\appendix
\begin{frame}{Reference}
\bibliographystyle{apacite}
\bibliography{refs}
\end{frame}
%--------------------------------------------------------------------------

>>>>

\renewcommand\bibliographytypesize{\tiny}
\DeclareMathOperator*{\argmax}{\arg\!\max}

@@

  \begin{eqnarray}
  \hat{\bm \theta}=\argmax_{\bm \theta} \ell(\bm \theta; x_{1}, \ldots, x_{n})\\
   s(\hat{{\bm \theta}}; \bm{x}_i) = \frac{\partial}{\partial \bm{\theta}} 
  \log
\text{L}({\bm{x}}_i, {\bm{\theta}}) \big |_{\bm{\theta} = \widehat{\bm{\theta}}}\\
  \displaystyle\sum_{i=1}^{n} s(\hat{\bm{\theta}} ; \bm{x}_i) =
  {\bm 0} 
  \end{eqnarray}

@@

\end{frame}
%--------------------------------------------------------------------------
\begin{frame}[fragile]
\frametitle{Procedures of Application}
\begin{enumerate}[3.]
  \suite
  \item Test of measurement invariance
\end{enumerate}
<<sctest-ord2, eval=FALSE>>=
 library(strucchange)
maxlmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4, 
               vcov = "info", functional = "maxLMo", 
               plot = TRUE)
@
<<sctest-ord2res, eval=TRUE>>=
maxlmo
@ 
\end{frame}
%--------------------------------------------------------------------------

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for the $\mathit{LM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics, fig.height=3.3, fig.width=5, echo=FALSE, results='hide'>>=
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = maxLMo, plot = TRUE, 
               ylim = c(0, 14), xlab = "Age group", 
               ylab = "LM statistics")
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
 \begin{itemize}
 \item Thanks! 
 \item Questions?
 \end{itemize}
\vspace{0.3in}
 Wang, T., Merkle, E. C., Zeileis, A. (2014). Score-based tests of measurement 
 invariance: Use in practice. \emph{Quantitative Psychology and Measurement},
 5, 438. 
\end{frame}
%--------------------------------------------------------------------------
\appendix
\begin{frame}{Reference}
\bibliographystyle{apacite}
\bibliography{refs}
\end{frame}
%--------------------------------------------------------------------------
